Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-08-18 stp/paper_aaai/main.tex
reduced figure a bit. Taken Natalia's responses to my questions into account. Still one page of free space

\begin{figure}[ht]
\centering
\begin{tikzpicture}
	\node[class] (pe) at (0,0)  {Person};
	\node[class] (co) at (0,-3) {Organisation};
	\node[class] (ev) at (3.5,1) {Event};
	\node[class] (pl) at (5,-1) {Place};
	\node[class] (ci) at (3,-3) {City};
	\node[class] (st) at (5,-3) {State};

@@

	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
	node [midway, below, sloped] {name} (-1,-5);
	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
	node [midway, above, sloped] {phone} (0,-5);
	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
	node [midway, above, sloped] {email} (1,-5);

	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
	node [midway, below, sloped] {startDate} (2.5,3.2);
	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
	node [midway, above, sloped] {endDate} (3.5,3.2);
	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
	node [midway, below, sloped] {title} (4.5,3.2);

@@

\ddg{IMPORTANT: Do we keep all of them, or only the top $k$ with most 
confidence? If so, 
what is $k$?}
\npr{We keep all, that is the crucial difference from Karma which does some voodoo heuristic filtering}

@@

The algorithm we used to construct $\mathcal{G_O}$ is the same as Taheriyan 
\etal{} and is described in detail in the cited paper 
\cite{taheriyan2016learning}.
Briefly, the algorithm has three parts:
\begin{enumerate}
\item Adding the known semantic models.
\item Adding the semantic types learned for the target source. \ddg{TODO: see 
Important note above}
\item Expanding the graph using the domain ontology $\mathcal{O}$.
\end{enumerate}

@@

Our goal is to take a set of graphs (the semantic models from the training set 
$S_T$) and find patterns that appear often across that set of graphs. This is 
known as the Frequent Subgraph Mining (FSM), which contains the subgraph 
isomorphism, known to be NP-complete. 
There exists a range of tools that can achieve this task using Transactional 
Frequent Graph Pattern Mining\cite{petermann2017dimspan,yan2002gspan}. 
We chose to use DIMSpan \cite{petermann2017dimspan}. 
\ddg{CHECK! How do they solve an NP-complete problem??}
\npr{Im not sure what to say here: there is just no guarantee how long it will take for the whole thing to run, except there is a threshold on how frequent they have to be; they use gSpan procedure to prune patterns and a variant of Ulmans algorithm for graph pattern matching}

@@

	\path[draw] (a4) -- (stn1);
	\path[draw] (a4) -- (cin1);
	\path[draw] (a4) -- (con1);
	\path[draw] (a4) -- (cin2);
	\path[draw] (a4) -- (con2);
\end{tikzpicture}
\caption{Example of integration graph. (`\tikz{ \node[att] () at (0,0)  
{};}' are attribute nodes). We omit weights for clarity. Data node labels are 
abbreviated but 
correspond to the ones shown in Fig \ref{FIG:ali}.}
\label{FIG:inte}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\begin{tikzpicture}
	\node[class] (pe) at (0,0)  {Person};
	\node[class] (co) at (0,-2.5) {Organisation};
	\node[class] (ev) at (3,0.5) {Event};
	\node[class] (pl) at (5,-1) {Place};
	\node[class] (ci) at (3,-2.5) {City};
	\node[class] (st) at (5,-2.5) {State};

@@

	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
	node [midway, below, sloped] {name} (-1,-4);
	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
	node [midway, above, sloped] {phone} (0,-4);
	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
	node [midway, above, sloped] {email} (1,-4);

	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
	node [midway, below, sloped] {startDate} (2.3,2.2);
	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
	node [midway, above, sloped] {endDate} (3.5,2.2);
	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
	node [midway, below, sloped] {title} (4.5,2);

@@

Note that we keep all the matches, regardless of the confidence fo the match. 
This is an important difference between our system and other approaches 
\cite{taheriyan2016learning} that 
remove some of the matches based on heuristics to then simplify the task of 
finding the semantic model.

%\ddg{IMPORTANT: Do we keep  all of them, or only the top $k$ with most 
%confidence? If so, 
%what is $k$?}
%\npr{We keep all, that is the crucial difference from Karma which does some 
%voodoo heuristic filtering}

@@

The algorithm we used to construct $\mathcal{G_O}$ is the same as Taheriyan 
\etal{} and is described in detail in the cited paper 
\cite{taheriyan2016learning}.
Briefly, the algorithm has three parts:
\begin{enumerate}
\item Adding the known semantic models.
\item Adding the semantic types learned for the target source. \ddg{If we keep 
all matches, isn't this just adding all the semantic types?}
\item Expanding the graph using the domain ontology $\mathcal{O}$.
\end{enumerate}

@@

Our goal is to take a set of graphs (the semantic models from the training set 
$S_T$) and find patterns that appear often across that set of graphs. This is 
known as the Frequent Subgraph Mining (FSM), which contains the subgraph 
isomorphism, known to be NP-complete. 
There exists a range of tools that can achieve this task using Transactional 
Frequent Graph Pattern Mining \cite{petermann2017dimspan,yan2002gspan}. 
We chose to use DIMSpan \cite{petermann2017dimspan}, which uses gSpan as a 
pruning procedure \cite{yan2002gspan}.
%\ddg{CHECK! How do they solve an NP-complete problem??}
%\npr{Im not sure what to say here: there is just no guarantee how long it will 
%take for the whole thing to run, except there is a threshold on how frequent 
%they have to be; they use gSpan procedure to prune patterns and a variant of 
%Ulmans algorithm for graph pattern matching}

@@

	\path[draw] (a4) -- (stn1);
	\path[draw] (a4) -- (cin1);
	\path[draw] (a4) -- (con1);
	\path[draw] (a4) -- (cin2);
	\path[draw] (a4) -- (con2);
\end{tikzpicture}
\caption{Example of integration graph. (`\tikz{ \node[att] () at (0,0)  
{};}' are attribute nodes). We omit weights and only show the most likely 
matches for clarity. Data node labels are 
abbreviated but 
correspond to the ones shown in Fig \ref{FIG:ali}.}
\label{FIG:inte}
\end{figure}
